FictionEro - Data Cleaning

### 2024-02-19 analysis/1_cleaning.qmd
update
free scale recruitment history plot

# Consecutive count of participants per day (as area)
df |>
  mutate(Date = as.Date(Date, format = "%d/%m/%Y")) |> 
  group_by(Date, Language, Experimenter) |> 
  summarize(N = n()) |> 
  ungroup() |>
  # https://bocoup.com/blog/padding-time-series-with-r
  complete(Date, Language, Experimenter, fill = list(N = 0)) |> 
  group_by(Language, Experimenter) |>
  mutate(N = cumsum(N)) |>
  ggplot(aes(x = Date, y = N)) +
  geom_area(aes(fill=Experimenter)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Recruitment History",
    x = "Date",
    y = "Total Number of Participants"
  ) +
  facet_wrap(~Language, nrow=3) +
  see::theme_modern()

@@

#### Dimension Stability

>>>>

# Consecutive count of participants per day (as area)
df |>
  mutate(Date = as.Date(Date, format = "%d/%m/%Y")) |> 
  group_by(Date, Language, Experimenter) |> 
  summarize(N = n()) |> 
  ungroup() |>
  # https://bocoup.com/blog/padding-time-series-with-r
  complete(Date, Language, Experimenter, fill = list(N = 0)) |> 
  group_by(Language, Experimenter) |>
  mutate(N = cumsum(N)) |>
  ggplot(aes(x = Date, y = N)) +
  geom_area(aes(fill=Experimenter)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Recruitment History",
    x = "Date",
    y = "Total Number of Participants"
  ) +
  facet_wrap(~Language, nrow=3, scales = "free_y") +
  see::theme_modern()

@@

#### Structure Stability
